
\chapter[Testing]{Testing}{Testing}\label{Test}
\noindent
\rule{0.49\textwidth}{0.75pt} $_{\bigcirc}$ \rule{0.49\textwidth}{0.75pt}\\
In DAVS, testing is essential to ensure the secure federated learning workflow behaves reliably under benign and adversarial conditions. Given the sensitivity of medical AI collaboration, the testing process focuses on verifying correctness of the training pipeline, stability of gradient sketching, robustness of committee selection, correctness of PBFT-inspired validation, and integrity of the blockchain audit trail.

Tests are performed across the end-to-end pipeline: client-side local training and update generation, Random Projection sketching and communication, DAVS scoring and committee selection, consensus voting and update acceptance/rejection, and audit logging of round metadata. Integration testing ensures that coordinator, validators, and ledger components remain consistent under different client participation and attacker ratios.

In addition, adversarial testing is carried out using multiple poisoning strategies (e.g., label flip, gradient flip, Gaussian noise injection, model scaling, and backdoor triggers). These tests validate that DAVS excludes malicious clients from the validator committee and that global model integrity is preserved through consensus and immutable logging.
\\
\noindent

\section{Test Cases}



\renewcommand{\arraystretch}{1.1}
\begin{center}
\textbf{Test Cases Overview}
\end{center}

\begin{longtable}{|p{1.1cm}|p{2cm}|p{2.5cm}|p{3cm}|p{3cm}|}
\hline
\textbf{Test Case ID} & \textbf{Feature} & \textbf{Test Scenario} & \textbf{Test Steps} & \textbf{Expected Result} \\
\hline
\endfirsthead

\hline
\textbf{Test Case ID} & \textbf{Feature} & \textbf{Test Scenario} & \textbf{Test Steps} & \textbf{Expected Result} \\
\hline
\endhead

\hline \multicolumn{5}{r}{\emph{Continued on next page}} \\
\endfoot

\hline
\endlastfoot

TC01 & Client Join & Validate client participation in a round & 1. Start client 2. Register with coordinator & Client joins and receives global model. \\
\hline
TC02 & Local Training & Validate local epochs and update creation & 1. Train for \(E\) epochs 2. Compute \(\Delta w_i\) & Local update computed correctly. \\
\hline
TC03 & Sketching & Validate Random Projection sketch generation & 1. Apply \(s_i = R \cdot \Delta w_i\) 2. Check dimension & Sketch dimension correct and finite. \\
\hline
TC04 & Transmission & Validate sketch transmission to coordinator & 1. Send sketch 2. Receive ACK/log & Coordinator receives sketch reliably. \\
\hline
TC05 & DAVS Scoring & Validate score computation and ranking & 1. Compute cosine similarities 2. Rank clients & Scores computed and ranked correctly. \\
\hline
TC06 & Committee Selection & Validate top-\(k\) committee formation & 1. Select top-\(k\) by score 2. Output committee & Committee generated; outliers excluded. \\
\hline
TC07 & PBFT Prepare & Validate validator update checks & 1. Check NaN/Inf 2. Check norms/thresholds & Validators produce consistent votes. \\
\hline
TC08 & PBFT Commit & Validate quorum-based acceptance & 1. Collect votes 2. Apply quorum rule & Update accepted/rejected correctly. \\
\hline
TC09 & Model Hashing & Validate global model hash generation & 1. Hash aggregated model 2. Compare logs & Hash deterministic and recorded. \\
\hline
TC10 & Ledger Append & Validate blockchain audit write & 1. Append block 2. Verify link/hash chain & Block written; chain remains valid. \\
\hline
TC11 & Attack Scenario & Validate resilience under poisoning & 1. Inject malicious clients 2. Run rounds & Accuracy degrades gracefully; attacks mitigated. \\
\hline
TC12 & Privacy Guarantee & Validate no raw data leakage & 1. Inspect network payloads 2. Confirm only sketches/metrics & No raw images/labels transmitted. \\
\hline
TC13 & Audit Integrity & Validate tamper-evidence of logs & 1. Verify hash chain 2. Detect modification & Tampering detected via hash mismatch. \\
\hline
\end{longtable}

\rule{0.49\textwidth}{0.75pt} $_{\bigcirc}$ \rule{0.49\textwidth}{0.75pt}\\



