\chapter[Introduction]{Introduction}{Introduction}\label{Intro}

\noindent
\rule{0.49\textwidth}{0.75pt} $_{\bigcirc}$ \rule{0.49\textwidth}{0.75pt}\\

Federated Learning (FL) has emerged as a promising paradigm for privacy-preserving collaborative model training in healthcare, enabling distributed medical institutions to jointly develop high-quality diagnostic models without centralizing sensitive patient data. However, practical deployment in clinical settings still faces three interrelated challenges: the communication burden caused by high-dimensional gradient exchange, vulnerability to Byzantine poisoning attacks under non-IID data, and the absence of verifiable training provenance for auditability.

This thesis presents DAVS, a unified framework that addresses these issues by combining Random Projection-based gradient sketching, a Data-Aware Verifier Selection mechanism, a PBFT-inspired consensus protocol, and a permissioned blockchain audit layer. The system is designed to reduce communication cost, improve robustness against malicious clients, and create an immutable record of model updates.

Unlike reputation-based systems that depend on historical behavior, DAVS makes decisions using the current round of gradient statistics. It evaluates directional alignment and magnitude consistency to identify representative and trustworthy clients for committee formation. This amnesic design helps the framework remain resilient to adaptive adversarial strategies such as trust-building and Flash Attacks.

\noindent

\section{Motivation / Objective}
The motivation for DAVS comes from the need to train medical AI models across multiple institutions without exposing raw patient data. In real deployments, hospitals often have different data distributions, limited bandwidth, and no direct way to verify whether participating nodes are honest. Standard FL systems can therefore become vulnerable to poisoned updates, unreliable contributors, and poor traceability. The objective of this project is to develop a secure and communication-efficient federated learning workflow that preserves privacy, resists malicious behavior, and records training activity in a verifiable manner.

\section{Proposed Solution}
The proposed solution is DAVS, a federated learning architecture that uses gradient sketching to compress client updates before transmission. The framework then applies data-aware verifier selection to identify a committee of representative clients based on sketch similarity and magnitude consistency. This committee executes PBFT-style consensus to validate the aggregated model update, and the approved result is stored on a permissioned blockchain for tamper-proof auditability. The final design ensures that model training can proceed in a distributed and trustworthy manner without sharing raw medical data.

\section{Scope of the Project}
DAVS is intended for distributed medical environments where privacy, robustness, and traceability are critical. The framework is suitable for medical imaging and other sensitive healthcare applications that involve non-IID data across institutions. It focuses on reducing communication overhead, defending against poisoning attacks, and enabling blockchain-backed audit trails. The current scope does not include deployment on public, permissionless chains or full treatment of all possible adversarial strategies, but it establishes a foundation for secure collaborative model training in regulated settings.

\section{Report Overview}
This report presents the design and implementation of DAVS as a blockchain-enabled federated learning system for secure medical imaging. It describes the problem of communication-heavy and attack-prone FL, the literature that motivates the work, the proposed architecture, and the security layer built around verifier selection and consensus. The later chapters discuss system design, implementation details, experimentation, results, and the overall contribution of the framework toward secure collaborative learning.

\rule{0.49\textwidth}{0.75pt} $_{\bigcirc}$ \rule{0.49\textwidth}{0.75pt}\\
