

\begin{titlepage}
   % \centering
    \vspace*{1cm}
    
    {\Large \begin{center}
        \textbf{Acknowledgement}
    \end{center}} } \\[1.5cm]

% We are sincerely thankful to Dwarkadas J Sanghvi College of Engineering for providing
% us with the opportunity to conduct research on the project titled "DAVS"
% We express our gratitude and deepest appreciation to our mentor, Mr. Vivek Deodeshmukh, who has assisted us in conducting the research for this project and guided us through each stage.
We take this opportunity to express our deep sense of gratitude to our project guide Mr. Vivek Deodeshmukh for his continuous guidance and encouragement throughout the duration of our project work. It is because of his experience and wonderful knowledge we were able to fulfil the requirement for the completion of this project within the stipulated time. We would also like to thank Dr. Narendra Shekokar, Vice Principal and Head of the Department Computer Science and Engineering (IoT and Cyber Security with Block Chain Technology) for his encouragement, whole-hearted cooperation and support.

We would also like to thank our Principal, Dr. Hari Vasudevan and the management of D.J. Sanghavi College of Engineering, Vile Parle (W), Mumbai for providing us with all the facilities and a work-friendly environment. We acknowledge by thanking the assistance provided by departmental staff, library, lab assistant lab attendants.
% We have learned extensively about federated learning, blockchain consensus, Byzantine fault tolerance, and cryptographic verification, and their applications in secure medical AI. This project has 
% deepened our understanding of both distributed machine learning vulnerabilities and the potential of 
% blockchain integration in ensuring secure collaborations. We hope that this paper provides valuable 
% insights into the intersection of federated learning and blockchain, contributing to the 
% ongoing discourse in secure healthcare AI. I would also like to thank all the project members.

\vspace{1cm}

\noindent
\textbf{Parshav Dedhia (60019220120)} \\
\textbf{Piyush Kumar (60019220127)} \\
\textbf{Praveen Lodhi  (60019220022)} \\
\textbf{Shourya Tamboskar (60019220131)} \\
